%!TEX root = main.tex

In this project, we aim to develop and implement a deep learning algorithm that takes a fingerprint image as an input and classify it into one of the five pattern class types of a) Arch; b) Tented Arch; c) Left Loop; d) Right Loop; or e) Whorl. 

\subsection{Feature Extraction}
%
We will first apply raw fingerprint images to train a CNN for classification. The outputs of some intermediate layer of CNN will be used as features for possibly a support vector machine classifier.

For CNN architecture, we will first use canonical architecture (such as 5 \textit{convolutional} + 3 \textit{fully-connected} in \textit{AlexNet} \cite{krizhevsky2012imagenet}).
%
We will then modify the CNN architecture to improve the performance.
%
\subsection{Classifier}
%
We will consider two classifiers. The first one is the prediction layer of CNN. The values in last layer indicates the predicted probabilities of each class.
%
The second one is support vector machine (SVM) whose input features comprise of the CNN’s middle or last layers.

\subsection{Data Augmentation}

%
To further improve the performance, we will use data augmentation technique to generate more training samples in order to increase the generalization ability of our model. 
%
The augmentation methods include image rotation, resizing and translation.

\subsection{Multi-Task Learning}

Multi-Task Learning (MTL)\cite{caruana1998multitask} aims to improve the performance of multiple classification tasks by learning them jointly.
%
In MTL, some tasks can benefit from auxiliary information which is introduced by other tasks and the performance is improved\cite{zhang2016learning}.
%
In our project, the network is trained to perform both the primary task (fingerprint type classification) and one or more auxiliary tasks. 
%
The classification task is expected to benefit from the auxiliary task by jointly training them together.
%
This process can also be viewed as incorporating human knowledge into to training procedure.

To obtain labels for auxiliary tasks, we will use existing methods. For example, orientation flow estimation in \cite{NFIQ}.
